---
  title       : Pearson Education Data
subtitle    : Input, Output and Socioeconomic Education Indicators from 1990 to 2015
author      : Luo Kangshun, Andy
job         : Education Statistician
framework   : io2012      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
  
  ## The Sidebar (2/5)
  
  From the sidebar, select a <b>Primary Education Indicator</b> and the years you wished to study. You can also select up to 2 countries for comparison in the time frame.

---
  
  ## Education Trends tab (3/5)
  In the <a href="https://erapryde.shinyapps.io/Pearson_Education_Indicators_Luo_Andy">App</a>, the description is loaded as well as the correlation with time.  
<br>
  ```{r message=F, echo=F, eval= T, warnings =F}
data2 <- read.csv("Consolidated.csv",na.strings = "NA")
data2 <- data2[!is.na(data2$value),]
data2 <- subset(data2, Index == "Human Development Index")
data3 <- subset(data2, Country == "SINGAPORE")
data2 <- subset(data2, Country == "FINLAND")
data3 <- rbind(data3,data2)
```

```{r message=F, echo=F, eval= T, warnings =F, fig.width = 10, fig.height = 6, fig.align='center'}
ggplot(data3,aes(y=value,x=Year,colour=Country))+
  geom_point()+geom_smooth(method='lm')+
  xlab("year")+
  ylab("Human Development Index")+
  theme_stata()+scale_colour_stata()+
  ggtitle("Human Development Index for SINGAPORE and FINLAND")+
  scale_x_continuous()
```


---
  
  ## Snapshot Analysis (4/5)
  Select a Year as well as another Indicator to correlate. Drag across groups of points and they display in the area below the chart.

```{r message=F, echo=F, eval= T}
data2 <- read.csv("Consolidated.csv",na.strings = "NA")
data2 <- data2[!is.na(data2$value),]
data2 <- subset(data2,Year == 2010)
data3 <- subset(data2, Index == "Human Development Index")
data2 <- subset(data2, Index == "Health Index")
data2 <- merge(data2,data3,by="Country")
```

```{r}
ggplot(data2,aes(y=value.y,x=value.x))+
  geom_point()+
  geom_smooth(method="lm")+
  xlab("Human Development Index")+
  ylab("Health Index")+
  theme_stata()+scale_colour_stata()+
  ggtitle("Health Index against Human Development Index for 2010")
```

---
  
  ## Education Data (5/5)
  
  Select a Country and indicator and the table displays.

```{r message=F, echo=F, eval= T, warnings =F, fig.width = 10, fig.height = 6, fig.align='center'}
data2 <- read.csv("Consolidated.csv",na.strings = "NA")
data2 <- subset(data2, Country == "SINGAPORE")
data2 <- subset(data2, Index =="Human Development Index")
```

```{r}
data2
```
